***De novo* clustering methods out-perform reference-based methods for assigning 16S rRNA gene sequences to operational taxonomic units**

### 2016-02-22 papers/peerj_2015/Schloss_Cluster_PeerJ_2015.Rmd
Not sure what's going on

---
title: "***De novo* clustering methods out-perform reference-based methods for assigning 16S rRNA gene sequences to operational taxonomic units**"
bibliography: references.bib
output:
  pdf_document:
    includes:
      in_header: header.tex
csl: peerj.csl
fontsize: 11pt
geometry: margin=1.0in
---

@@

\includepdf{results/figures/figure_1.pdf}
\includepdf{results/figures/figure_2.pdf}
\includepdf{results/figures/figure_3.pdf}
\includepdf{results/figures/figure_4.pdf}
\includepdf{results/figures/figure_5.pdf}

>>>>

---
title: "***De novo* clustering methods out-perform reference-based methods for assigning 16S rRNA gene sequences to operational taxonomic units**"
bibliography: references.bib
output:
  pdf_document:
    includes:
      in_header: ../header.tex
csl: peerj.csl
fontsize: 11pt
geometry: margin=1.0in
---

@@

\includepdf{../../results/figures/figure_1.pdf}
\includepdf{../../results/figures/figure_2.pdf}
\includepdf{../../results/figures/figure_3.pdf}
\includepdf{../../results/figures/figure_4.pdf}
\includepdf{../../results/figures/figure_5.pdf}
